Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-10 trunk/lids/twittersearchwrap/paper/paper.tex

The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
The corpus contains evaluation results solicited via Mechanical Turk.
In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.
@@@even with hashtags we have ambiguity, how would be map Twitter message containing the keyword ``apple''?

Softic et al \cite{key:softic} have developed a framework and system for mining
data from social networks. They have instantiated their system to analyze data from Twitter. In their system, they collect data from one or several users. The system by Passant et al. \cite{key:smob} is used for transforming twitter data to semantic data. The triplified data can then be analysed using SPARQL. They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
As such, our approach is closely related.
Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages.
% from stakovic et al.
%In order to make tweets more searchable and make them useful for the described
%scenario one would need to have represent them in a structured format and associate
%those tweets with the topics that refer to. As a basic approach we process the text of
%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
%concepts related to a tweet, but is useful only on a limited number of tweets directly
%mentioning a particular topic. In the example data set we produced from ESWC2010,
%tweet topics are represented using dc:subject property.

Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.
The system we use for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
The so-called Wikifier maps text to Wikipedia pages, which in turn directly map to DBpedia URIs.

@@

Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks. They have instantiated their system to analyze data from Twitter. In their system, they collect data from one or several users. The system by Passant et al. \cite{key:smob} is used for transforming Twitter data to semantic data. The triplified data can then be analysed using SPARQL. They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.

@@

Topics trending worldwide and in Germany on Twitter retrieved on February 24th
17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
constitute a basis of input search terms for our evaluation of the Twitter
Search Wrapper.

We have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to
2011-03-06.
The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}.
We then recorded search results for these 50 hashtags during the course of 24 hours (2011-03-07).

@@

\begin{table}[ht*]
\centering
\begin{tabular}{ |l|l| }
\hline
\textsc{Trending Topic} & \textsc{Location}  \\
\hline
\#goodlucknickj & Worldwide \\
\#smalljoys & Worldwide \\
\#thingsthedevilinvented & Worldwide \\
Adam Wainwright & Worldwide \\
CatchPetrovaFire & Worldwide \\
Gadafi & Worldwide \\
Libia & Worldwide \\
Precious Minaj & Worldwide \\
Tommy John & Worldwide \\
\hline
\#gaddafi & Germany \\
\#guttenberg & Germany \\
\#libya & Germany \\
Doktorarbeit & Germany \\
Gef\"{u}hl & Germany \\
Lion & Germany \\
MBP & Germany \\
Thunderbolt & Germany \\
Vorratsdatenspeicherung & Germany \\
\hline
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

\myremark{todo}{Deutsche Themen nicht ausgewertet wegen Sprachproblem}

>>>>

Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks. They have instantiated their system to analyze data from Twitter. In their system, they collect data from one or several users. The system by Passant et al. \cite{key:smob} is used for transforming twitter data to semantic data. The triplified data can then be analysed using SPARQL. They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.

Relating semantic concepts with twitter messages has been attempted by various authors:
Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages. 
% from stakovic et al.
%In order to make tweets more searchable and make them useful for the described
%scenario one would need to have represent them in a structured format and associate
%those tweets with the topics that refer to. As a basic approach we process the text of
%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
%concepts related to a tweet, but is useful only on a limited number of tweets directly
%mentioning a particular topic. In the example data set we produced from ESWC2010,
%tweet topics are represented using dc:subject property.
Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.

Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction. As such, our approach is closely related.

@@

The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
The corpus contains evaluation results solicited via Mechanical Turk. In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.

@@

We have conducted the evaluation on two sets of queries: the first set are the trending topics worldwide and in Germany on Twitter retrieved on February 24th 17:20h (GMT) -- these topics are listed in Table \ref{tbl:terms}. Trending topics are chosen as they cover a variety of recently talked about topics which due to its recent nature may be of high interest for further processing.

\begin{table}[ht*]
\centering
\begin{tabular}{ l }
Trending Topics Worldwide  \\
\hline
\#goodlucknickj  \\
\#smalljoys \\
\#thingsthedevilinvented \\
Adam Wainwright  \\
CatchPetrovaFire \\
Gadafi  \\
Libia \\
Precious Minaj \\
Tommy John  \\
\end{tabular}
\begin{tabular}{l}
Trending Topics Germany \\
\hline
\#gaddafi \\
\#guttenberg  \\
\#libya  \\
Doktorarbeit \\
Gef\"{u}hl  \\
Lion  \\
MBP \\
Thunderbolt \\
Vorratsdatenspeicherung \\
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

The second query set consists of hash tags that are frequently used on Twitter. To obtain these, we have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}.

@@

The goal of our evaluation was to examine the stability of the entity annotations over time. To achieve this, we have repeatedly executed the same set of queries and analysed the returned data.

In principle, two methods for data acquisition were identified: \begin{definition}[Data Acquisition Methods]
\begin{itemize}
\item {\bf Temporal Sliding Window}\newline The query is executed and the n
most recent results are retrieved every t minutes. The Temporal Sliding Window
method may lead to duplicate messages in the retrieved documents, but needs to
handle much less data and allows for an analysis over larger time frames.
\item {\bf $k$-item Sliding Window}\newline  The k-item Sliding Window methods
retrieves all messages that match the query exactly one time. Each time k new messages are
available matching the given query a document containing those k messages
is retrieved. This method can lead to high data volume and needs constant
monitoring of recently posted messages matching the search term.
\end{itemize}
\end{definition}

The disadvantage of the first method is that it is neither possible to guarantee that all messages matching the search are collected, nor is it possible to avoid overlaps between the search results. However, while the second method seems to overcome these problems, it does not: Using the $k$-item sliding window method, it is not clear when the next search result should be fetched: even when frequently querying for new messages, if updates are frequent it is likely to lack messages in the result set.

For both data set queries were executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame. Data for the trending topics was collected on 2011-02-24, for the frequent hash tags data was collected on 2011-03-07.
